HTW E1 Testing

### 2023-10-09 Analysis/e1_test.qmd

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

@@

```{=tex}
\begin{equation}
dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
\end{equation}
```
```{r}
#| label: tbl-e1-test-nf-deviation
#| tbl-cap: "Testing Deviation - Empirical Summary"
#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
#| layout-ncol: 2
#| echo: fenced

result <- test_summary_table(test, "dist", mfun = list(mean = mean, median = median, sd = sd))
result$constant
result$varied
```

@@

The model predicting absolute deviation (dist) showed clear effects of both training condition and target velocity band (Table X). Overall, the varied training group showed a larger deviation relative to the constant training group (β = 135, 95% CI \[43, 231\]). Deviation also depended on target velocity band, with lower bands showing less deviation. See @tbl-e1-bmm-dist for full model output.

@@

@@

@@

```{=tex}
\begin{equation}
vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
\end{equation}
```
```{r}
#| label: fig-e1-test-vx
#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9
test %>% group_by(id,vb,condit) |> plot_distByCondit()

@@

result <- test_summary_table(test, "vx", mfun = list(mean = mean, median = median, sd = sd))
result$constant 
result$varied

@@

modelName <- "e1_extrap_testVxBand"
e1_extrap_VxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                  data=test |>
                    filter(expMode=="test-Nf"),file=paste0(here::here("data/model_cache",modelName)),
                  iter=5000,chains=4)
GetModelStats(e1_extrap_VxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to 3 extrapolation bands")
```

See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition (β = 164.67, 95% CrI \[45.50, 278.85\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination. Most relevant to the issue of discrimination is the slope on Velocity Band (β = 0.71, 95% CrI \[.62, .80\]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The estimate for the interaction between slope and condition (β = -.14, 95% CI \[-.26, -0.01\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less senitivity between vands than the constant condition. This difference is depicted visually in @fig-e1-bmm-vx.@tbl-e1-slope-quartile shows the average slope coefficients for varied and constant participants separately for each quartile. The constant participant participants appear to have larger slopes across quartiles, but the difference between conditions may be less pronounced for the top quartiles of subjects who show the strongest discrimination. Figure @fig-e1-bmm-bx2 shows the distributions of slope values for each participant, and the compares the probability density of slope coefficients between training conditions. @fig-e1-indv-slopes

The second model, which focused solely on extrapolation bands, revealed similar patterns. The Velocity Band term (β = 0.50, 95% CrI 0.42,0.570.42,0.57) still demonstrates a high degree of discrimination ability. However, the posterior distribution for interaction term (β = -0.07, 95% \[CrI −0.17,0.04\] ) does across over 0, suggesting that the evidence for decreased discrimination ability for the varied participants is not as strong when considering only the three extrapolation bands.

@@

 shows the distributions of estimated slopes relating velocity band to x velocity for each participant, ordered from lowest to highest within condition. Slope values are lower overall for varied training compared to constant training. Figure Xb plots the density of these slopes for each condition. The distribution for varied training has more mass at lower values than the constant training distribution. Both figures illustrate the model's estimate that varied training resulted in less discrimination between velocity bands, evidenced by lower slopes on average.

>>>>

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

@@

```{=tex}
\begin{equation}
dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
\end{equation}
```

```{r}
#| label: tbl-e1-test-nf-deviation
#| tbl-cap: "Testing Deviation - Empirical Summary"
#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
#| layout-ncol: 2
#| echo: fenced

result <- test_summary_table(test, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
result$constant
result$varied
```

@@

@@

coef_details <- broom.mixed::tidy(e1_distBMM) |>
  filter(term == "conditVaried") |> 
  select(estimate, conf.low, conf.high) |> mutate(across(where(is.numeric), \(x) round(x, 2)))

@@

The model predicting absolute deviation (dist) showed clear effects of both training condition and target velocity band (Table X). Overall, the varied training group showed a larger deviation relative to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]). Deviation also depended on target velocity band, with lower bands showing less deviation. See @tbl-e1-bmm-dist for full model output.

@@

```{=tex}
\begin{equation}
vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
\end{equation}
```

$k(x,x') = \exp \left( - \frac{\|x - x'\|^2}{2\lambda^2} \right)$

```{r}
#| label: fig-e1-test-vx
#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9
test %>% group_by(id,vb,condit) |> plot_distByCondit()

@@

result <- test_summary_table(test, "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
result$constant 
result$varied

@@

cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
sc1 <- get_coef_details(e1_vxBMM, "bandInt")
intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")

modelName <- "e1_extrap_testVxBand"
e1_extrap_VxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                  data=test |>
                    filter(expMode=="test-Nf"),file=paste0(here::here("data/model_cache",modelName)),
                  iter=5000,chains=4)
GetModelStats(e1_extrap_VxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to 3 extrapolation bands")

sc2 <- get_coef_details(e1_extrap_VxBMM, "bandInt")
intCoef2 <- get_coef_details(e1_extrap_VxBMM, "conditVaried:bandInt")

See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination. Most relevant to the issue of discrimination is the slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The estimate for the interaction between slope and condition (β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less senitivity between vands than the constant condition. This difference is depicted visually in @fig-e1-bmm-vx.@tbl-e1-slope-quartile shows the average slope coefficients for varied and constant participants separately for each quartile. The constant participant participants appear to have larger slopes across quartiles, but the difference between conditions may be less pronounced for the top quartiles of subjects who show the strongest discrimination. Figure @fig-e1-bmm-bx2 shows the distributions of slope values for each participant, and the compares the probability density of slope coefficients between training conditions. @fig-e1-indv-slopes

The second model, which focused solely on extrapolation bands, revealed similar patterns. The Velocity Band term (β = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]) still demonstrates a high degree of discrimination ability. However, the posterior distribution for interaction term (β = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\] ) does across over 0, suggesting that the evidence for decreased discrimination ability for the varied participants is not as strong when considering only the three extrapolation bands.

@@

@fig-e1-bmm-bx2 shows the distributions of estimated slopes relating velocity band to x velocity for each participant, ordered from lowest to highest within condition. Slope values are lower overall for varied training compared to constant training. Figure Xb plots the density of these slopes for each condition. The distribution for varied training has more mass at lower values than the constant training distribution. Both figures illustrate the model's estimate that varied training resulted in less discrimination between velocity bands, evidenced by lower slopes on average.
